Figures

### 2019-05-17 figures/06_lulc_buffer_demo.Rmd
add raster resolution fig

>>>>

```{r raster_resolution}
library(nadp)

llid  <- 2745

iws   <- query_gis("IWS", "lagoslakeid", llid)
n_dep <- nadp_load("2010", "totalN")
n_dep <- raster::crop(n_dep, as_Spatial(st_as_sfc(st_bbox(iws))))
n_dep <- mask(n_dep, iws)

# create a baseflow grid of 1000m and a ndep grid of 2338 m
gg_dep_grid <- ggplot() + 
  geom_sf(data = iws) +
  geom_sf(data = st_make_grid(iws, cellsize = 2338), alpha = 0) +
  coord_sf(datum = NA) +
  theme_void()

gg_bf_grid <- ggplot() + 
  geom_sf(data = iws) +
  geom_sf(data = st_make_grid(
    st_buffer(st_as_sfc(st_bbox(st_make_grid(iws, cellsize = 2338))), 400), 
                    cellsize = 1000), 
    alpha = 0) +
  coord_sf(datum = NA) +
  theme_void()

cowplot::plot_grid(gg_dep_grid, gg_bf_grid)
```
